Object-Oriented Internet\\ Cloud Interoperability

### 2021-01-03 Latex/ICCS21MPostoOOIGateway2Azure/ICCS21MPostoOOIGateway2Azure.tex
References #23
- added all references from existing bib file ( ICCS20 ).

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach. In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, any human interaction must be recognized as impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.

@@

Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect. \ref{subs.architecture}).

@@

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. Prototyping addresses Microsoft Azure Cloud as an example. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640}.

@@

To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP or IP and has to support the OPC UA Information Model. As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow. To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected. OPC UA supports the following two patterns to be used to transfer data between communicating parties:

@@

Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT, AMQP, and HTTP. A software development kits for C\#, Java, PHP, and Ruby are available for custom applications. Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14. Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.

@@

The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} implementing the \emph{IBindingFactory} interface. It captures functionality responsible for accessing the external process data from \emph{LocalResources}. The \emph{LocalResources} represents an external part that has a very broad usage purpose. For example, it may be any kind of the process data source/destination, i.e. raw data (e.g. PLC internal registers), OPC UA Address Space Management, cloud, file, database, graphical user interface, to name only a few.

@@

The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.

>>>>

A typical \textbf{human-centric} approach is a web-service supporting, for example, a web user interface (UI) to monitor conditions and manage millions of devices and their data in a typical cloud-based IoT approach \cite{RefWorks:doc:5d87d02be4b0e88bdacab9a7, RefWorks:doc:5d87d1c9e4b0bc72a68d7b46, RefWorks:doc:5d9216c9e4b03ba5e075a855}. In this case, it is characteristic that any uncertainty and necessity to make a decision can be relaxed by human interaction. Coordination of robots behavior in a work-cell (automation islands) is a \textbf{machine-centric} example. In this case, any human interaction must be recognized as impractical or even impossible. This interconnection scenario requires the machine to machine communication (M2M) \cite{RefWorks:doc:5d6cdbbbe4b082ad50f3a83e, mpostol2020, RefWorks:doc:5d8f6d9ee4b058d660094a94, RefWorks:doc:5d868e46e4b030b4e0569e60, RefWorks:doc:5d8f7275e4b0bc72a68f4dcb} demanding multi-vendor devices integration.

@@

Deployment of the hybrid solution providing interoperability of the \textbf{machine - centric} Cyber-Physical System (CPS) \cite{RefWorks:doc:5c458659e4b014f3944f6969} and \textbf{human - centric} cloud-based front-end can be implemented applying the following scenarios: \textbf{direct} or \textbf{gateway} based interconnection (Sect. \ref{subs.architecture}).

@@

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment OPC Unified Architecture \cite{RefWorks:doc:5ac86c99e4b009947bbb87c6, LiteratureSurveyOnOpenPlatformCommunications, RefWorks:doc:5ac86c99e4b009947bbb87d2} interoperability standard has been selected. Prototyping addresses Microsoft Azure Cloud as an example. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{mariusz_postol_2020_4361640}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet (OOI) \cite{mariusz_postol_2020_4361640, RefWorks:doc:5c6912c9e4b0a562a3fc7f5b, RefWorks:doc:5c66740ae4b081adf5804596}.

@@

To comply with the Industry 4.0 communication criterion it is required that any product must be addressable over the network via TCP/UDP \cite{RefWorks:doc:5d8e1874e4b0bc72a68f0d11} or IP \cite{RefWorks:doc:5ac86c98e4b009947bbb8730} and has to support the OPC UA Information Model \cite{OPCUAPart5, RefWorks:doc:5ac86c99e4b009947bbb87c9, RefWorks:doc:5d986a28e4b0b0c862c0d184}. As a result, any product being advertised as Industry 4.0 enabled must be OPC UA-capable somehow. To support the multi-vendor environment OPC Unified Architecture interoperability standard has been selected. OPC UA supports the following two patterns to be used to transfer data between communicating parties:

@@

Azure aids Internet protocols and open standards such as JSON, XML, SOAP, REST, MQTT\cite{RefWorks:doc:5d91e158e4b02eb43d36bb97}, AMQP\cite{RefWorks:doc:5d91d2d9e4b0bc72a68ffe06}, and HTTP. A software development kits for C\#, Java, PHP, and Ruby are available for custom applications. Azure provides services supporting data exchange over the OPC UA, but they don't support PubSub compliant with the OPC UA Part-14. Connectivity services on the network use JSON-based Data Transfer Object encoded based on schema derived from the solution metadata.

@@

The \emph{DataRepository} represents data holding assets in the \emph{Reactive Application} implementing the \emph{IBindingFactory} interface. It captures functionality responsible for accessing the external process data from \emph{LocalResources}. The \emph{LocalResources} represents an external part that has a very broad usage purpose. For example, it may be any kind of the process data source/destination, i.e. raw data (e.g. PLC internal registers), OPC UA Address Space Management \cite{mpostol2020}, cloud, file, database, graphical user interface, to name only a few.

@@

The described results prove that the \emph{Embedded Gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} \cite{RefWorks:doc:5ac86c97e4b009947bbb8728} embedded component of the OPC UA Server. The real challenge of the future work is to prove that the proposed solution is flexible enough to be used as an archetype to embed the \emph{Embedded Gateway} component into the OPC UA Client or Server to get connected with the cloud in case of the interactive relationship.
